*Bromus* Density Dependence Analysis

### 2019-09-15 Scripts/BromusRollingUpdateFile.Rmd
Test for interaction term

## Updatre status
This update uses the expanded data set from Alden and Catherine and cleans up the coefficients in the quadratic function

@@

```{r}
model_saturated <- summary(lm(data=final_df,r~poly(snow_cover,2, raw=TRUE) +
                                              poly(win_precip_snow,2, raw=TRUE) +
                                              poly(win_precip_tot,2, raw=TRUE) +
                                              poly(win_precip_rain,2, raw=TRUE) +
                                              poly(grow_seas_precip_rain,2, raw=TRUE) +
                                              poly(density,1)))

@@

```{r}
model_reduced <- summary(lm(data=final_df,r~poly(snow_cover,2, raw=TRUE) +
                                              poly(win_precip_snow,2, raw=TRUE) +
                                              poly(win_precip_tot,2, raw=TRUE) +
                                              poly(density,1)))

@@

```{r}
model_reduced2 <- summary(lm(data=final_df,r~poly(snow_cover,2, raw=TRUE) +
                                              poly(win_precip_rain,2, raw=TRUE) +
                                              poly(density,1)))

@@

>>>>

## 15 September 2019
This update adds raw to all poly statements, tries adding an interaction term for snow and precip, and constructs heat maps for visualizing the Hutchinsonian niche.

## Update status
This update uses the expanded data set from Alden and Catherine and cleans up the coefficients in the quadratic function

@@

```{r}
model_saturated <- summary(lm(data=final_df,r~poly(snow_cover,2, raw=TRUE) +
                                              poly(win_precip_snow,2, raw=TRUE) +
                                              poly(win_precip_tot,2, raw=TRUE) +
                                              poly(win_precip_rain,2, raw=TRUE) +
                                              poly(grow_seas_precip_rain,2, raw=TRUE) +
                                              poly(density,1, raw=TRUE)))

@@

```{r}
model_reduced <- summary(lm(data=final_df,r~poly(snow_cover,2, raw=TRUE) +
                                              poly(win_precip_snow,2, raw=TRUE) +
                                              poly(win_precip_tot,2, raw=TRUE) +
                                              poly(density,1, raw=TRUE)))

@@

```{r}
model_reduced2 <- summary(lm(data=final_df,r~poly(snow_cover,2, raw=TRUE) +
                                              poly(win_precip_rain,2, raw=TRUE) +
                                              poly(density,1, raw=TRUE)))

@@

## Reduced model with interaction term

For this model, we will try an interaction between the linear components of snow cover and rain

```{r}
model_reduced3 <- summary(lm(data=final_df,r~poly(snow_cover,2, raw=TRUE) +
                                              poly(win_precip_rain,2, raw=TRUE) +
                                              poly(density,1, raw=TRUE) + 
                                              snow_cover:win_precip_rain))

print(model_reduced3)
```

Since the interaction term doesn't add anything, we will not include it and stick with the simple reduced model.

## Heat map for visualizing lambda values
